Adopting agile in the large: motivations, success factors and challenges

### 2013-12-13 journal/article.tex
Reasons to change analysis

>>>>

\subsection{Reasons to change}

Problems
xxxxxxxxxx     Overhead in process, the process is found to be ineffective
xxx            Current processes are not taken seriously (followed)
xxxxxxxxxxxx   Dysfunction in managing software development
xx             Lack of flexibility
xxxxxxxxx      Quality issues
xx             Bad visibility and feedback of projects
xxxxxxxxxxxxx  Difficulties to schedule or estimate software development, problems with deadlines
x              Lack of knowledge transfer
xx             Motivation and morale problems
xxxx           Difficulties in customer relations and communication
x              Problems meeting business needs

x  Demand for speed (TTM)
